SunPy - Python for Solar Physics

### 2014-01-24 2-2-Lightcurve.tex

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{{pycon}
>>> print lyra.data
<class pandas.core.frame.DataFrame>
DatetimeIndex: 1496629 entries, 2011-01-28 00:00:00.110000 to 
2011-01-28 23:59:59.983993
Data columns (total 4 columns):
CHANNEL1    1496629  non-null values
CHANNEL2    1496629  non-null values
CHANNEL3    1496629  non-null values
CHANNEL4    1496629  non-null values
dtypes: float64(4)

>>>>

\begin{listing}[H]
\begin{minted}[bgcolor=bg]{pycon}
>>> print lyra.data
<class pandas.core.frame.DataFrame>
DatetimeIndex: 1496629 entries, 2011-01-28 00:00:00.110000 to 
2011-01-28 23:59:59.983993
Data columns (total 4 columns):
CHANNEL1    1496629  non-null values
CHANNEL2    1496629  non-null values
CHANNEL3    1496629  non-null values
CHANNEL4    1496629  non-null values
dtypes: float64(4)
